Our device falls into one main category, electrical and electronic test equipment market. This market includes industrial testing of products as well as educational uses in colleges and universities. According to Mordor Intelligence, a market intelligence and advisory firm, the compound annual growth rate of the market size for electrical and electronic test equipment is expected to grow by 4.2\%, going from \$13.81 billion and reaching \$17.48 billion by the year 2029 \cite{mordor2023}. Some of the major players within this market are Fortive, Keysight, and NI. IBISWorld, another provider of industry research reports and market intelligence, reported that the market size for the testing and educational support industry in the U.S. was \$37.1 billion in 2023 \cite{ibisworld2023}.

\subsection{National Instruments (NI)}
National Instruments (NI) has been in business for 48 years and is the developer of the ELVIS board with an estimated revenue of \$1.02 billion. On the 3rd of Oct. 2023, they were acquired by Emerson and became part of Emerson's Test and Measurement group \cite{emerson2023}. These boards have a variety of features, but the ones we intend to improve upon would be the logic analyzer and signal generation. The NI ELVIS III has 16 logic analyzer/signal generators, eight less than what we intend to have on our device. The NI ELVIS III has a price of \$2799, which is far beyond what our projected price will be \cite{ni2023}.

\subsection{Digilent}
Digilent has been in business for 24 years and provides a variety of FPGAs with an estimated \$4.2 million dollar revenue. While Digilent provides several boards to choose from, these boards lack the breadboard component that the ELVIS board comes with, have little to no data analysis, and still have a price range from \$150 to \$2000 depending on the board and accompanying features \cite{digilent2023}. Looking at one Digilent product in particular, the Analog Discovery 2, this product offers many features but the ones our product will be exceeding are the number of logic analyzers available and the configurations provided for the power supply. The Analog Discovery 2 has 16 logic analyzers which, like the ELVIS board, are eight less than what we intend to supply. Another issue is the limited power options that the Analog Discovery 2 has, limited to two power supplies ranging from 0V to +5V and 0V to -5V. Our product will be able to provide a much higher power supply to its applications, extending the overall usefulness of our product \cite{analog2023}.

\subsection{Vernier}
Vernier has been in business for 43 years with an estimated revenue of \$30 million and offers a variety of devices for educational engineering activities. One such product is their LabQuest series, which provide data analysis. However, these products cost \$400, and the sensors for the data analysis device are not included. Furthermore, their products do not provide the breadboard base for building a circuit nor the wave generation that our product will have \cite{vernier2023}.

\subsection{Comparing Main Features of Our Product}
The main features of our product will be 24 analog logic analyzer channels, 24 signal generator channels, and the ability to select the power on the output pins from 15V, 10V, 5V, and 3.3V. These features would allow our product to perform multiple forms of analysis and testing at the same time, such as plotting I-V curves for semiconductors while performing logic analysis at various points in a circuit. The results of the data analysis will be shown on screen for viewing by the user. This aspect covers most everything that a student will do or may desire to do in labs or for projects for learning circuit and system analysis. Industry use for our product will likely be connected to developing devices to our device and using our device to input a variety of signals into the device under test to determine the results and see if the tested device is performing as intended. With an estimated \$500 retail cost, our product will be less than half the cost of comparable oscilloscopes, such as the DHO1204 at \$1400, with additional signal generator and logic analyzer features.
