\begin{thebibliography}{99}
	
	\bibitem{mordor2023}
	“Electrical and Electronic Test Equipment Market Size \& Share Analysis – Growth Trends \& Forecasts (2024 – 2029),” MordorIntelligence.com. Accessed: May 3, 2024. [Online.] Available: \url{https://www.mordorintelligence.com/industry-reports/electrical-and-electronic-test-equipment-market}
	
	\bibitem{ibisworld2023}
	“Testing \& Educational Support in the US – Market Size (2005- 2030),” IBISWorld.com. Accessed: May 3, 2024. [Online.] Available: \url{https://www.ibisworld.com/industry-statistics/market-size/testing-educational-support-united-states/}
	
	\bibitem{emerson2023}
	NI.com. Accessed: May 3, 2024. [Online.] Available: \url{https://www.ni.com/en/about-ni.html}
	
	\bibitem{ni2023}
	W. Wong. “Third Time’s the Charm with Elvis III,” ElectronicDesign.com. Accessed: May 3, 2024. [Online.] Available: \url{https://www.electronicdesign.com/technologies/embedded/article/21807299/third-time-is-a-charm-with-elvis-iii}
	
	\bibitem{digilent2023}
	Digilent.com. Accessed: May 3, 2024. [Online.] Available: \url{https://digilent.com/search-result/?search_query=Development\%20boards}
	
	\bibitem{analog2023}
	A. Williams. “Review: Digilent Analog Discovery 2,” Hackaday.com. Accessed: May 3, 2024. [Online.] Available: \url{https://hackaday.com/2016/12/28/review-digilent-analog-discovery-2/}
	
	\bibitem{vernier2023}
	Vernier.com. Accessed: May 3, 2024. [Online.] Available: \url{https://www.vernier.com/product/labquest-3/}
	
	\bibitem{ngscope_intro}
	“Streamline hardware test,” ngscopeclient.
	\url{https://www.ngscopeclient.org }
\end{thebibliography}
‌